Measurement of ($\pi^-$-Ar) and ($K^+$-Ar) total hadronic cross sections in the LArIAT experiment

### 2018-05-30 Chapter-1/1-Theory.tex
s

\chapter{The theoretical framework}

@@

{\raggedleft -- J. S. Bach, Suite No. 1 in G major, BWV 1007, 1720 ca. -- \par}
\vspace{0.5cm}

@@

\subsubsection{$\pi^{-}$Ar Hadronic Interaction: Signal Signatures}
Strong hadronic interaction models \cite{9780198520085,9780471779957} predict the pion interaction processes with argon in the [100 - 1200] MeV energy range. 
The total hadronic $\pi^{-}$-Ar interaction cross section is defined as the one related to the single process driven only by the strong interaction which is dominant in the considered energy range. 
In measuring the ``total" cross section, we include both the elastic and  reaction channels, regardless of the final state, 
\begin{equation}
\sigma_{Tot} = \sigma_{Elastic}+ \sigma_{Reaction};
\end{equation}
the reaction channel is further characterized by several exclusive channels with defined topologies,
\begin{equation}
\sigma_{Reaction} = \sigma_{Inelastic} + \sigma_{abs} + \sigma_{chex}+ \sigma_{\pi prod}.
\end{equation}

>>>>

\chapter{The theoretical framework}\label{ch:TheTheory}

@@

{\raggedleft -- J. S. Bach, 1720 ca. -- \par} %, Suite No. 1 in G major, BWV 1007
\vspace{0.5cm}

@@

\subsubsection{$\pi^{-}$Ar Hadronic Interaction: Signal Signatures}\label{ch:signature}
Strong hadronic interaction models \cite{9780198520085,9780471779957} predict the pion interaction processes with argon in the [100 - 1200] MeV energy range. 
The total hadronic $\pi^{-}$-Ar interaction cross section is defined as the one related to the single process driven only by the strong interaction which is dominant in the considered energy range. 
In measuring the ``total" cross section, we include both the elastic and  reaction channels, regardless of the final state, 
\begin{equation}
\sigma_{Tot} = \sigma_{Elastic}+ \sigma_{Reaction};
\end{equation}
the reaction channel is further characterized by several exclusive channels with defined topologies,
\begin{equation}
\sigma_{Reaction} = \sigma_{Inelastic} + \sigma_{abs} + \sigma_{chex}+ \sigma_{\pi prod}.
\end{equation}
